\documentclass[letterpaper,12pt,addpoints]{exam}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{amssymb}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[shortlabels]{enumitem}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{environ}
\usepackage{float}
\usepackage{dirtytalk}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath, amssymb, amsfonts, amsthm}

\DeclareMathOperator*{\argmin}{arg\,min}

% Declare Operators
\newcommand{\wv}{\mathbf{w}}
\newcommand{\bias}{b}
\newcommand{\xv}{\mathbf{x}}
\newcommand{\slack}{\xi}
\newcommand{\const}{C}
\newcommand{\margin}{M}
\newcommand{\kernel}{K}
\newcommand{\kernelmap}{\phi}
\newcommand{\param}{\gamma}
\newcommand{\st}{\mathop{\mathrm{subject\,\,to}}}

\newcommand{\ns}[1]{{\color{red}\bf NS: #1}}

\renewcommand\questionlabel{\thequestion)} %replace period with parenthesis
\renewcommand{\thequestion}{\bfseries\large\arabic{question}}

\newcommand\stoplabeling{\def\makelabel##1{}}
\newcommand\resumelabeling{\def\makelabel##1{\hss\llap{##1}}}
\nopointsinmargin
\pointformat{}


% SOLUTION environment
\NewEnviron{soln}{
\leavevmode\color{red}\ignorespaces \textbf{Solution} \BODY }{}

\title{10-715 Fall 2020 Homeworks}

\begin{document}


\begin{center}
{\Large CMU 10-715: Final Exam}\\
{\bf DUE: Dec. 16, 2020, 11:40 AM Eastern Standard Time}.\\
\end{center}

\textbf{\large Instructions}:

\begin{itemize}
    \item It is a 24-hour exam. The submission site will close at 11:40 AM, Dec 16.

    \item You can refer to your own notes, the scribe notes, homework solutions, the text book, and lecture videos. You are \textbf{NOT} allowed to use any other resources (e.g., no searching on the Internet).
    
    \item You are \textbf{NOT} allowed to discuss the exam with anyone in the duration of the exam. For any questions, please post on Diderot.
    
    \item For the programming question(s), you can feel free to use any code you wrote for any of the homeworks. 
    
    \item Submit your solutions in a pdf file to Gradescope. Handwritten or typed solutions are both accepted. Start \textbf{each question on a new} page and make sure you select the corresponding page(s) for each question during submission to Gradescope. 
    
    \item We recommend taking a brief look at all questions first and then starting to answer them. You may find some questions easier than others. Good luck!
\end{itemize}

\begin{center}
\textbf{Distribution of Marks}\\
\medskip
\gradetable[v][questions]
\end{center}

\newpage
\begin{questions}
\question[10]
\section*{Neural Networks and Circuit Building Blocks \textcolor{red}{[10]}} 
\input{final/section1_neural_building_blocks.tex}
\addpoints

\newpage
\question[10]
\section*{Graphical models, causality, and Dr. X \textcolor{red}{[10]}} 
\input{final/section2_graphical_models.tex}
\addpoints

\newpage
\question[10]
\section*{Learning with Experts and Power of Two Choices \textcolor{red}{[10]}} 
\input{final/section3_experts_and_two_choices.tex}
\addpoints

\newpage
\question[10]
\section*{Adversarial Machine Learning \textcolor{red}{[10]}} 
\input{final/section4_adversarial.tex}
\addpoints

\newpage
\question[10]
\section*{Categorical Log Likelihood and Cross Entropy \textcolor{red}{[10]}}
\input{final/section5_categorical_cross_entropy.tex}
\addpoints

\newpage
\question[10]
\section*{Shapley Values and ML Interpretability \textcolor{red}{[10]}} 
\input{final/section6_shapley_interpretability.tex}
\addpoints

\newpage
\question[10]
\section*{A Bayesian approach to Multi-armed Bandits \textcolor{red}{[10]}}
\input{final/section7_thompson_sampling.tex}
\addpoints

\end{questions}
\end{document}