\documentclass[letterpaper,12pt,addpoints]{exam}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{amssymb}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[shortlabels]{enumitem}
\usepackage{bm}
\usepackage{graphicx}

\DeclareMathOperator*{\argmin}{arg\,min}

% Declare Operators
\newcommand{\wv}{\mathbf{w}}
\newcommand{\bias}{b}
\newcommand{\xv}{\mathbf{x}}
\newcommand{\slack}{\xi}
\newcommand{\const}{C}
\newcommand{\margin}{M}
\newcommand{\kernel}{K}
\newcommand{\kernelmap}{\phi}
\newcommand{\param}{\gamma}
\newcommand{\st}{\mathop{\mathrm{subject\,\,to}}}

\newcommand{\ns}[1]{{\color{red}\bf NS: #1}}

\renewcommand\questionlabel{\thequestion)} %replace period with parenthesis
\renewcommand{\thequestion}{\bfseries\large\arabic{question}}

\newcommand\stoplabeling{\def\makelabel##1{}}
\newcommand\resumelabeling{\def\makelabel##1{\hss\llap{##1}}}
\nopointsinmargin
\pointformat{}

\usepackage[utf8]{inputenc}

\title{10-715 Fall 2020 Homeworks}

\begin{document}


\begin{center}
{\Large CMU 10-715: Midterm Exam}\\
{\bf DUE: Oct. 8, 2020, 11:40 AM Eastern time}.\\
\end{center}

\textbf{\large Instructions}:

\begin{itemize}
    \item It is a 24-hour exam. The submission site will close at 11:40 AM, Oct 8.

    \item You can refer to your own notes, the scribe notes, homework solutions, the text book, and lecture videos. You are \textbf{NOT} allowed to use any other resources (e.g., no searching on the Internet).
    
    \item You are \textbf{NOT} allowed to discuss the exam with anyone in the duration of the exam. For any questions, please post on Diderot.
    
    \item For the programming question(s), you can feel free to use any code you wrote for any of the homeworks. 
    
    \item Submit your solutions in a pdf file to Gradescope. Handwritten or typed solutions are both accepted. Start \textbf{each question on a new} page and make sure you select the corresponding page(s) for each question during submission to Gradescope. 
    
    \item We recommend taking a brief look at all questions first and then starting to answer them. You may find some questions easier than others. Good luck!
\end{itemize}

\begin{center}
\textbf{Distribution of Marks}\\
\medskip
\gradetable[v][questions]
\end{center}

\newpage
\begin{questions}
\question[10]
\section*{Enthusiastic Data Augmentation [10 pts]}
\input{midterm/section1_enthusiastic_data_augment.tex}
\addpoints

\newpage
\question
\section*{Perceptron on Non Linearly Separable Data [10 pts]}
\input{midterm/section2_not_separable_perceptron.tex}

\newpage
\question
\section*{Kernel Soft SVM implementation [25 pts]}
\input{midterm/section3_kernel_softSVM_implementation.tex}

\newpage
\question[10]
\section*{Kernelizable Objectives and  the Representer Theorem [10 pts] }
\input{midterm/section4_representer_theorem.tex}
\addpoints

\newpage
\question[10]
\section*{Validity of a Kernel [10 pts]}
\input{midterm/section5_valid_kernel.tex}
\addpoints

\newpage
\question[15]
\section*{Epsilon-net Arguments [15 pts]}
\input{midterm/section6_epsilon.tex}
\addpoints

\newpage
\question[15]
\section*{PAC Learnable [15 pts]}
\input{midterm/section7_pac_learnable.tex}
\addpoints

\newpage
\question
\section*{No Free Lunch Theorem [15 pts]}
\input{midterm/section8_free_lunch.tex}

\end{questions}

\end{document}